\documentclass[a4paper]{article}
\usepackage[margin=50pt]{geometry}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{multicol}
\pagestyle{empty}
\title{Project Law Report}
\author{Web Apps Group 08 \\ Elliot Greenwood, Paul Li\'etar, Michael Radigan \& Jamie Lane}
\date{}
\setlength{\droptitle}{-5em}
\begin{document}
\maketitle

\section{Summary}
The only sections which require comment are LGPL and GPL. We are justified in using these as we are not distributing. We would be within our rights to distribute however as we are dynamically linking. We are hosting our application on heroku and are therefore subject to the terms and conditions of their free plan. As we are doing this purely for educational purposes we are completely within these bounds.

\section{List of packages by license}

\subsection{BSD/MIT/Apache 2.0}
	For our purpose, these licenses are similar enough that they can be considered equivalent. Particular attention has been paid to codemirror, sweetalert and jquery as we distribute the source for these files. We are able to do so within the bounds of the license as bundle.js reserves the copyright information.

\begin{itemize}
\begin{multicols}{3}
	\item antage/eventsource
	\item fsnotify/fsnotify
	\item gopherjs
	\item gorilla/*
	\item kardianos/osext 
	\item lib/pq 
	\item lucasb-eyer/go-colorful
	\item namsral/flag
	\item neelance/sourcemap
	\item nu7hatch/gouuid
	\item spf13/cobra
	\item spf13/pflag
	\item stretchr/testify
	\item ugorji/go
	\item kevinbeaty/any-promise
	\item petkaantonov/bluebird
	\item substack/browserify
	\item codemirror/codemirror
	\item debuglog
	\item eventstream
	\item gulpjs/gulp
	\item gulp-sass
	\item gulp-typescript
	\item gulp-typings
	\item jquery
	\item sass-module-importer
	\item sweetalert
	\item tsify
	\item vinyl-source-stream
	\item rust-lang
	\item go-lang
	\item mruby
	\item typescript
	\item \_buttons.scss
	\item bootstrap
	\item various rust libraries
	\item tailhook/quick-error
	\item plietar/*
	\item egnwd/*	
\end{multicols}
\end{itemize}
\subsection{LGPL}
\begin{itemize}
\item libseccomp
\end{itemize}
\subsection{GPL}
\begin{itemize}
\item gcc
\item bash
\item linux
\end{itemize}

\end{document}

